Exception Handling Bug Hazards in Android

### 2015-10-09 SPRINGER_JOURNAL/msr_journal.tex
fixing typos

\begin{abstract}
This paper reports two studies:  a repository mining study whose goal was to identify 
exception handling bug hazards in Android apps; and an exploratory survey study - whose goal
was to assess the perspectives of developers conserning such bug hazards.
The repository mining study mined the exception stack traces embedded on 
159,048 issues reported on Android projects hosted in GitHub (482 projs.) 
and Googlecode (157 projs.).  Overall 6,005 exception stack traces were extracted, 
and analyzed in combination with source code and bytecode analysis. 
Some bug hazards were consistently detected such as:  unexpected exception wrappings (e.g., Errors being wrapped in checked exceptions), and NullPointerExeptions as the major cause of reported chashes in about 50\% of all analyzed projects. Finally, a survey was applied to some developers 
involved on such GitHub projects and their perspective about the bug hazards and 
how they deal with them as assessed and discussed.

@@

The number of mobile apps is increasing in a daily rate. If on the one hand they
extend phones capabilities far beyond of the basic calls, on the other hand they have to 
cope with an increasing number of exceptinal conditions 
(e.g., faults in underlying middleware or hardware; compatibility issues~\cite{McDon13}; 
memory and battery restrictions; noisy external resources~\cite{Zhang12}).

>>>>

\begin{abstract}
This paper reports two studies:  a repository mining study whose goal was to identify 
exception handling bug hazards in Android apps; and an exploratory survey study - whose goal
was to assess the perspectives of developers concerning such bug hazards.
The repository mining study mined the exception stack traces embedded on 
159,048 issues reported on Android projects hosted in GitHub (482 projs.) 
and Googlecode (157 projs.).  Overall 6,005 exception stack traces were extracted, 
and analyzed in combination with source code and bytecode analysis. 
Some bug hazards were consistently detected such as:  unexpected exception wrappings 
(e.g., Errors being wrapped in checked exceptions), and NullPointerExeptions 
as the major cause of reported crashes - reported in 
28\% of all mined stack traces found in about 50\% of all analyzed projects. 
Finally, a survey was applied to some developers 
involved on some of the GitHub Android projects analyzed in our study 
and their perspective about the bug hazards and 
how they deal with them was assessed and discussed.

@@

The number of mobile apps is increasing in a daily rate. If on the one hand they
extend phones capabilities far beyond of the basic calls, on the other hand they have to 
cope with an increasing number of exceptional conditions 
(e.g., faults in underlying middleware or hardware; compatibility issues~\cite{McDon13}; 
memory and battery restrictions; noisy external resources~\cite{Zhang12}).
